---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
library(ggplot2)
library(knitr)
library(magrittr)
library(kableExtra)
library(chron)
rawdata <- read.csv("./activity/activity.csv")
activities <- na.omit(rawdata)
```

## What is the total number of steps taken per day?

```{r}
totalSteps <- aggregate(activities$steps, by=list(date=activities$date), FUN=sum)
colnames(totalSteps) <- c("Date", "Steps")
ggplot(totalSteps, aes(x=Steps)) + geom_histogram(binwidth = 1000, fill = "blue", colour = "grey60", size=0.2) + labs(title=expression("Total number of steps taken each day"))
```   
   
__The mean of total number of steps per day__
```{r}
meanTotalStepsPerDay <- aggregate(activities$steps, by=list(date=activities$date), FUN=mean)
kable(meanTotalStepsPerDay, "html") %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
    scroll_box(width = "500px", height = "200px")
```   
   
__The median of total number of steps per day__
```{r}
medianTotalStepsPerDay <- aggregate(activities$steps, by=list(date=activities$date), FUN=median)
kable(meanTotalStepsPerDay, "html") %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
    scroll_box(width = "500px", height = "200px")
```

## What is the average daily activity pattern?
```{r}
intervalStepsAllDays <- aggregate(activities$steps, list(activities$interval), mean)
colnames(intervalStepsAllDays) <- c("Interval", "Steps")
ggplot(intervalStepsAllDays, aes(Interval, Steps)) + geom_line() +
    labs(title=expression("Steps of Each 5-minute Intervals Across All Days"))
```
   
__The 5-minute interval with the Maximal steps on average__ 
```{r}
maxSteps <- intervalStepsAllDays[which.max(intervalStepsAllDays$Steps), ]
kable(maxSteps, "html") %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

## Imputing missing values
```{r}
totalNAs <- sum(is.na(rawdata$steps))
```
__The total number of NAs is: `r totalNAs`__            
__Since the median value steps of all days are 0, I'll just replace the NAs by 0.__
```{r}
NAfilledData <- rawdata
NAfilledData$steps[is.na(NAfilledData$steps)] <- 0

imputedTotalSteps <- aggregate(NAfilledData$steps, by=list(date=NAfilledData$date), FUN=sum)
colnames(imputedTotalSteps) <- c("Date", "Steps")
ggplot(imputedTotalSteps, aes(x=Steps)) + geom_histogram(binwidth = 1000, fill = "green", colour = "black", size=0.2) + labs(title=expression("Total number of steps taken each day(Imputed data)"))
```
  
  __With imputed data, the mean of total number of steps per day__
```{r}
newMeanStepsPerDay <- aggregate(NAfilledData$steps, by=list(date=NAfilledData$date), FUN=mean)
kable(newMeanStepsPerDay, "html") %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
    scroll_box(width = "500px", height = "200px")
```   
  
__With imputed data, the median of total number of steps per day__
```{r}
newMedianStepsPerDay <- aggregate(NAfilledData$steps, by=list(date=NAfilledData$date), FUN=median)
kable(newMedianStepsPerDay, "html") %>% 
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
    scroll_box(width = "500px", height = "200px")
```   
  
## Are there differences in activity patterns between weekdays and weekends?

```{r}
newData <- NAfilledData
newData$Days <- ifelse(is.weekend(newData$date),"weekend", "weekday")
newTotalSteps <- aggregate(newData$steps, list(as.numeric(newData$interval), newData$Days), FUN=mean)
colnames(newTotalSteps) <- c("Interval", "Day", "Steps")

ggplot(newTotalSteps, aes(Interval, Steps, Day)) + geom_line() + 
    facet_grid(. ~ Day) +
    labs(title=expression("Average Steps of 5-minute Intervals"))
```
